\Title

### 2021-06-03 manuscript/content.tex
Add results of eql-boost on airborne survey to manuscript

\subsection{Window size and overlap in gradient boosting}

@@

>>>>

\subsection{Window size and overlap in gradient boosting}
\label{sec:window_size_and_overlap}

@@

\subsection{
    Interpolating synthetic survey with gradient boosting
}

Finally we used gradient-boosted equivalent sources to interpolate the
synthetic airborne survey. We started by locating a set of block-averaged
equivalent sources using a block size of \EqlBoostAirborneSpacing{} and, based
on the results presented on section \ref{sec:window_size_and_overlap}, we
decided to use an overlap of 50\% and a window size of
\EqlBoostAirborneWindowSize{} in order to define a considerable amount of
windows.

We estimated the \emph{depth} and \emph{damping} parameters by comparing the
predictions against the values of the target grid, exploring \emph{depth}
values between \EqlBoostAirborneMinDepth{} and \EqlBoostAirborneMaxDepth{} and
\emph{damping} values between \EqlBoostAirborneMinDamping{} and
\EqlBoostAirborneMaxDamping{} by steps of one order of magnitude.
The most accurate predictions achieved a RMS error of
\EqlBoostAirborneRmsScore{} with a depth of \EqlBoostAirborneDepth{} and
a damping of \EqlBoostAirborneDamping{}.

Figure \ref{fig:eql-boost-airborne}a shows the difference between the target
grid and the predictions made by the gradient-boosted equivalent sources.
Figure \ref{fig:eql-boost-airborne}b shows the RMS error of the
residuals after each iteration, exposing how the gradient-boosting algorithm
converges to a minimum fitting error.

\begin{figure}
    \includegraphics[width=\linewidth]{figs/eql-boost-airborne.pdf}
    \caption{
        Results of interpolating the airborne synthetic survey with
        gradient-boosted equivalent sources.
        a)~Pseudo-color maps of the differences between the target grid and the
        interpolated synthetic airborne survey data produced gradient-boosted
        equivalent sources.
        b)~Root-mean squared error of the residuals after each iteration of the
        gradient-boosting algorithm.
}
\label{fig:eql-boost-airborne}
\end{figure}
